Differential invariant signatures for planar Lie group transformations of images

### 2019-11-06 paper/newpaper.tex
Now with some real words...

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (1) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants up to weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants}
\end{table}

@@

@@

Ignoring translation, the action of $SE(2)$ is simply rotation by some angle $\theta$, i.e.,

@@

\begin{align}
I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
I_4 &= f_x^2 f_{xx} - 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
\end{align}

However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$. Which is the product of 2 invariants in Einstein summation, but a pain in the arse any other way. But I can't see how else to get $f_{ii}$!

@@

>>>>

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (1) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
    \draw[-] (1) to [out=10,in=170] (2);
    \draw[-] (1) to [out=-10,in=-170] (2);
\end{tikzpicture}
& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to [out=-90,in=150] (3);
    \draw[-] (1) to [out=-30,in=90] (3);
\end{tikzpicture}
& $ f_{xx}^2 f_{yyyy} + 2 f_{xx} f_{yy} f_{xxyy} - 4 f_{xx} f_{xy} f_{xyyy} - 4 f_{yy} f_{xy} f_{xxxy} + 4 f_{xy}^2 f_{xxyy} + f_{xxxx} f_{yy}^2$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture} 
& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants up to weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants}
\end{table}

\todo[inline]{Put into 2 tables: order 2 + products, order 3, rest order 4. Then explain a little bit.}

@@

For $A(2)$ the weight of the partial transvectants prevents them from being invariants. They can be normalised by choosing only those where all components have the same weight and projecting them onto a unit hypersphere. Instead, we select ratios of partial transvectants. It is beneficial to choose the numerator and denominator so that they have different critical points, which can be achieved by adding together partial transvectants of the same weight as appropriate.

====

We consider as our image, the following function, defined on $[-1, 1]
\times:
[-1, 1]$
\begin{equation}\label{eq:function}
  \begin{split}
    f(x, y) &= 0.5 - 0.2x - 0.3y - 0.05x^2 + 0.03xy + 0.04y^2 \\ 
    &+ 0.03y^3 + 0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3.
  \end{split}
\end{equation}
This function was chosen to have no critical points, and to be
predominantly linear, so that the higher order derivatives were not too
large. This was predominantly so the higher order terms in the signatures
would not overwhelm the smaller terms. The function is depicted as a
greyscale image in Figure~\ref{fig:function}
\begin{figure}
  \centering
  \includegraphics[width=12cm]{figures/function}
  \caption{The test function used in this document, from
  Eq.~\eqref{eq:function}.}\label{fig:function}
\end{figure}

We consider the signatures of this function under various transformation
groups, as detailed throughout the main body of the paper and illustrate
the signature in three dimensions. A grid is overlaid on the image of the
function itself, as shown in Fig~\ref{fig:function_scanlines}. This grid is
mapped to the signature surface to help understand what the signature looks
like locally.
\begin{figure}
  \centering
  \includegraphics[width=12cm]{figures/function_scanlines}
  \caption{The test function used in this document, from
  Eq.~\eqref{eq:function} with a grid of lines
overlaid.}\label{fig:function_scanlines}
\end{figure}

@@

\todo[inline]{Make precise!}
Ignoring translation, the action of $SE(2)$ on the first derivatives is simply rotation by some angle $\theta$, i.e.,

@@

\begin{align}
I_2 &= f_x^2 f_{xx} + 2 f_x f_y f_{xy} + f_y^2 f_{yy} \\
I_3 &= f_x f_y (f_{yy} - f_{xx}) + f_{xy} (f_x^2 - f_y^2) \\
I_4 &= f_x^2 f_{xx} - 2 f_x f_y f_{xy} + f_y^2 f_{yy} 
\end{align}

\todo[inline]{Richard: Check if the summation and negation (!) of I2 and I4 are actually invariants.} Then we can write this bit. 
I3 is Robert's one.}
%However, summing $I_2$ and $I_4$ we can write the expression as $f_x^2 f_{xx} + f_y^2 f_{yy}$. Which is the product of 2 invariants in Einstein summation, but a pain in the arse any other way. But I can't see how else to get $f_{ii}$!

\todo[inline]{E(2) is confusing. Robert did it by contraction, and got nice invariants. For the moving frame, the issue is that you have to consider one of the branches, since there is a reflection ambiguity. This is hacked in the PSL(3,R) case. Even then, it isn't clear that you can get the nice ones. The same issue stands for trying to extend SE(2) to E(2).

Question: is there an extension of transvectants (change of operator) that lets you get to it that way?

However... we should do Sim(2) by adding a scaling to E(2), so we need it :(
}

@@

\todo[inline]{Richard to find the moving frame version!}
